Stable Hot Spot Analysis (Draft)

### 2017-06-17 paper-main.tex
minor fixes

% Focal size  
%	Increase of focal size leads to better results in the upward property
% 	Standard deviation decrease with higher focal size 
%	No standard deviation af F 17x17 because of missing clusters
%	The downward property reaches its maximum at 65x65
%
%	Conclusion: F should be around 65x65 or higher
\subsection{Impact of study area}
The first parameter we want to isolate is the size of the study area. This enables us to discuss the optimal size of the study area for the given research/decision question. 
To do so, we have to fix the focal size F and use it as the x-axis and plot the mean value as well as the mean +- the standard deviations of the SoH for all other parameter combinations as the y-axis.
In this scenario, only the Focal $G^*$ can produce varied results as the standard $G^*$ has by definition a fixed study area by always using the total size of the study area. 
In figure ~\ref{fig:SoHFocal} the \SOHUP and \SOHDOWN is shown for $G^*$ and Focal $G^*$.
Higher values indicate that the found hot spots are more stable. 
The \SOHUP in figure ~\ref{fig:fUp} growth with an increase of the focal size.
It can see that an increase of the focal size leads to better results for \SOHUP. 
With a higher focal size you can see that the dotted line, which represent the standard deviation, is getting smaller. This indicates that an increase in the size of the study area does not only lead to an overall increase of stability but also that the it reduces the volatility of the variations in other parameters.
When F and W have similar size, there are no clusters. Because the values have no much variation. 
\SOHDOWN (figure ~\ref{fig:fDown})shows a different picture then the \SOHUP.
It reaches its maximum SoH for a focal size F of 65x65 in our evaluation set. 
The standard deviation is not decreasing with an increase of the 
focal size.

@@

\begin{figure}[htp]
  \begin{subfigure}{\linewidth}
    \caption{SoH up for weight size}
    \includegraphics[width=\linewidth]{images/gen-weight-1}
    \label{fig:wUp}
  \end{subfigure}
  \hspace{1em}
  \begin{subfigure}{\linewidth}
    \caption{SoH down for weight size}
    \includegraphics[width=\linewidth]{images/gen-weight-2}
    \label{fig:wDown}
  \end{subfigure}
  \caption{SoH for weight size}
  \label{fig:SoHWeight}
\end{figure}
%
% Zoom
%	G* alwas better than Focal G* for upward and downward property
%	Focal G* has different focal sizes because zoom is compared
%	At zoom level 4 G* increase much more than Focal G*
%
%	Conclusion: G* is better than Focal G* in the zoom dimension, but the focal size is fixed. The zoom dimension has the least 
%	influence on the value
\subsection{Impact of Aggregation level}
Finally, we isolate the impact of the different aggregation levels on the stability of the hot spot analysis. 
We fix the aggregation and use it as x-axis. This allows us to examine the impact
the resolution of a data set has on the results and allow us indirectly to reduce the 
computational effort on future computations by using the maximal aggregation as useful.
The results can seen in figure ~\ref{fig:SoHZoom}.
First, we can see that for the aggregation level, in contrast to previous 
results, the standard $G^*$ seems to be more stable.

@@

With this work we made a step further to the optimal parametrisation for $G^*$ and Focal $G^*$.
Our results indicate that the parametrisation for $G^*$ and Focal $G^*$ besides what is defined as parent and child has a huge impact on the
stability of hotspots. We can see the increase of up to 0.6 \SOHUP for e.g. the focal matrix size.
This emphasizes the importance of a metric for the stability of hotspots. But this work also shows the shortcomings of the existing metric, as the trade-off between \SOHUP and \SOHDOWN is not yet fully explored and should be the focus of future work. 
Another interesting field for future research is the stability of spatio-temporal hot spots and their different parametrizations. As $G^*$ is often applied with regard to temporal impacts, the efficient computation of the focal $G^*$ for spatio-temporal and the impact on stability is the second main path for future research. 
We evaluated our data on the aggregate of a singular month, but one could assume that at lunchtime there will be hotspots at restaurants and they are not consistent with the hotspots over one month. Therefore the impact of time on the results is important and could also influence the metric for stability in profound ways. As in the example the question is, how fine grained should the temporal clustering be and when is the result unstable for useful reasons? 
This leads to the final future work: To which hot spots should the comparison be made for the metric? In the current state only the next parametrization is compared for computational time reasons. How the comparison hot spots should be chosen and how many different comparisons have to be used is another quite interesting question for future work.

\section{Acknowledgements}
This work is part of the research project BigGIS (reference number: 01IS14012)
funded by the Federal Ministry of Education and Research (BMBF) within the
frame of the programme "Management and Analysis of Big Data" in "ICT 2020 --
Research for Innovations".
%
\noindent R-packages used: \verb|raster|~\cite{cran:raster}, 
\verb|knitr|~\cite{cran:knitr}

>>>>

% Focal size  
%	Increase of focal size leads to better results in the upward property
% 	Standard deviation decrease with higher focal size 
%	No standard deviation af F 17x17 because of missing clusters
%	The downward property reaches its maximum at 65x65
%
%	Conclusion: F should be around 65x65 or higher
\subsection{Impact of study area}
The first parameter we want to isolate is the size of the study area. This enables us to discuss the optimal size of the study area for the given research/decision question. 
To do so, we have to fix the focal size F and use it as the x-axis and plot the 
mean value as well as the mean +/- the standard deviations of the SoH for all 
other parameter combinations as the y-axis.
In this scenario, only the Focal $G^*$ can produce varied results as the standard $G^*$ has by definition a fixed study area by always using the total size of the study area. 
In Figure~\ref{fig:SoHFocal} the \SOHUP and \SOHDOWN is shown for $G^*$ and 
Focal $G^*$.
Higher values indicate that the hot spots found are more stable. 
The \SOHUP in Figure~\ref{fig:fUp} growth with an increase of the focal size.
It can see that an increase of the focal size leads to better results for \SOHUP. 
With a higher focal size you can see that the dotted line, which represent the standard deviation, is getting smaller. This indicates that an increase in the size of the study area does not only lead to an overall increase of stability but also that the it reduces the volatility of the variations in other parameters.
When F and W have similar size, there are no clusters. Because the values have no much variation. 
\SOHDOWN (Figure ~\ref{fig:fDown}) shows a different picture then the \SOHUP.
It reaches its maximum SoH for a focal size F of 65x65 in our evaluation set. 
The standard deviation is not decreasing with an increase of the 
focal size.

@@

\begin{figure}[htp]
  \begin{subfigure}{\linewidth}
    \caption{SoH up for weight size}
    \includegraphics[width=\linewidth]{images/gen-weight-1}
    \label{fig:wUp}
  \end{subfigure}
  \hspace{1em}
  \begin{subfigure}{\linewidth}
    \caption{SoH down for weight size}
    \includegraphics[width=\linewidth]{images/gen-weight-2}
    \label{fig:wDown}
  \end{subfigure}
  \caption{SoH for weight size}
  \label{fig:SoHWeight}
\end{figure}
%
% Zoom
%	G* alwas better than Focal G* for upward and downward property
%	Focal G* has different focal sizes because zoom is compared
%	At zoom level 4 G* increase much more than Focal G*
%
%	Conclusion: G* is better than Focal G* in the zoom dimension, but the focal size is fixed. The zoom dimension has the least 
%	influence on the value
\subsection{Impact of Aggregation level}
Finally, we isolate the impact of the different aggregation levels on the stability of the hot spot analysis. 
We fix the aggregation and use it as x-axis. This allows us to examine the impact
the resolution of a data set has on the results and allow us indirectly to reduce the 
computational effort on future computations by using the maximal aggregation as useful.
The results can seen in Figure~\ref{fig:SoHZoom}.
First, we can see that for the aggregation level, in contrast to previous 
results, the standard $G^*$ seems to be more stable.

@@

With this work, we made a step further to the optimal parametrisation for $G^*$ 
and Focal $G^*$.
Our results indicate that the parametrization for $G^*$ and Focal $G^*$ besides 
what is defined as parent and child has a huge impact on the
stability of hotspots. We can see the increase of up to 0.6 \SOHUP for e.g. the focal matrix size.
This emphasizes the importance of a metric for the stability of hotspots. But this work also shows the shortcomings of the existing metric, as the trade-off between \SOHUP and \SOHDOWN is not yet fully explored and should be the focus of future work. 
Another interesting field for future research is the stability of spatio-temporal hot spots and their different parametrizations. As $G^*$ is often applied with regard to temporal impacts, the efficient computation of the focal $G^*$ for spatio-temporal and the impact on stability is the second main path for future research. 
We evaluated our data on the aggregate of a single month, but one could assume 
that during the lunchtime there will be hotspots at restaurants and they are 
not 
consistent with the hotspots over one month. Therefore the impact of time on 
the results is important and could also influence the metric for stability in 
profound ways. As in the example, the question is, how fine grained should the 
temporal clustering be and when is the result unstable? 
This leads to the final future work: To which hot spots should the comparison 
be made for the metric? In the current state, only the next parametrization is 
compared due to the high computational complexity. How the comparison of hot 
spots should be carried out and how many different comparisons have to be used 
is another quite interesting research question.

\section{Acknowledgements}
This work is part of the research project BigGIS (reference number: 01IS14012)
funded by the Federal Ministry of Education and Research (BMBF) within the
frame of the programme "Management and Analysis of Big Data" in "ICT 2020 --
Research for Innovations".
%
\noindent R-packages used: \verb|raster|~\cite{cran:raster}, 
\verb|knitr|~\cite{cran:knitr},
